Um novo modelo de avaliação para o curso de Engenharia de Produção

### 2024-05-29 manuscript/evaluation/manuscript.tex
Practical Based Learning - Students Evaluation - new idea for working with

\journal{Computers \& Industrial Engineering}

@@

\title{An exact method for the multi-product p-batch processing time maximization problem}

@@

\begin{abstract} 
Among the most complex multi-product batch problems are the multi-product p-batch scheduling (MPBS) problems, where jobs must be scheduled on parallel batch processing machines. When applying some local search heuristics to solve a MPBS problem, it can be necessary to iteratively solve a single stage multi-product p-batch sizing problem with different processing rates for different products, limited capacity units, and storage capacity defined both for each product and for all products. In this paper we name this problem multi-product p-batch processing time maximization (MBPTM) problem. Once a MBPTM problem needs to be solved in each iteration, the efficiency of the method developed for solving it has a huge impact on the computational cost of the local search algorithm used to solve some MPPBS problems. In addition, for some industries, efficiently solving a MBPTM problem can have a significant impact on storage costs and customer satisfaction. In this paper we present a mathematical model and an exact method with polynomial time complexity for the MBPTM problem. We developed a LINGO solver for solving the mathematic model, and a C ++ solver for application of the proposed exact method. We tested both solvers, comparing the results for a series of benchmarks with sizes varying between small and very large. As result, we find that the exact method can obtain optimal solutions in a very short time (just few seconds), even when solving very large instances. 
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item taxonomy and notation for the multi-product batch problems;
\item multi-product p-batch processing time maximization (MBPTM) problem definition;
\item integer programming model for the MBPTM problem;
\item exact optimization method for solving the MBPTM problem;
\item important inventory control support for some industries.
\end{highlights}

>>>>

\journal{XXX}

@@

\title{Um novo modelo de avaliação para o curso de Engenharia de Produção}

@@

\begin{abstract} 
Este artigo apresenta um modelo de avaliação semestral baseado no processo seletivo de empresas multinacionais a na abordagem metodologica Aprendizado Baseado na Prática. 
\end{abstract}
%%Graphical abstract
%\begin{graphicalabstract}
%\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item xxx
\end{highlights}
